---
title: "Interactive Figure"
author: "Camilla Salwen"
date: "2023-01-31"
output:
  prettydoc ::html_pretty:
    theme: cayman
    highlight: github
editor_options: 
  chunk_output_type: inline
---

## How to make an interactive graph!!!

1. add _interactive to the geom function you are using
  + for example geom_col --> geom_col_interactive
2. add an aes() in the geom function
  + this will include tooltip = and data_id =
  + put the column name whose info you want to be shown when you hover over the point/bar/etc
    + for example, tooltip = Mean.Sepal.Length, data_id = Mean.Sepal Length
    + the input should be the same for both tooltip and data_id
3. use the girafe() function
  + this is written after/outside the code to make your plot
  + in the parentheses, write ggobj = name of your plot
  + the width_svg and height_svg determine the dimensions of the figure
    + play around with them to find the dimensions that work best for your specific graph


```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(ggiraph)
library(patchwork)
```

## Example:

### Manipulating the data to show mean sepal length for each species
```{r}
d <- iris

Means <- iris %>%
  group_by(Species) %>%
  summarize(Mean.Sepal.Length = mean(Sepal.Length, na.rm = TRUE), N = n())
```

### Creating a simple bar graph with the data
```{r}
p3 <- ggplot(data = Means, aes(x=Species, y= Mean.Sepal.Length)) +
  geom_col (linewidth = 2, color = "black", fill = "skyblue") + 
  xlab("Species") +
  ylab("Mean Sepal Length")
p3
```

    
### Graph with the ggiraph extension
```{r}
p3interactive <- ggplot(data = Means, aes(x=Species, y= Mean.Sepal.Length)) +
  geom_col_interactive (linewidth =1, color = "black", fill = "skyblue", aes(tooltip = Mean.Sepal.Length, data_id = Mean.Sepal.Length)) + 
  xlab("Species") +
  ylab("Mean Sepal Length")

girafe(ggobj = p3interactive, width_svg = 7, height_svg = 4)
```

